\documentclass[NETN,manuscript]{stjour-new}
\setcounter{secnumdepth}{1}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{pbox}
\usepackage{afterpage}
\usepackage{makecell}
\usepackage{fourier} 
\usepackage{array}
\usepackage{xr}
\usepackage{cleveref}
\usepackage{tikz-cd}
\usepackage{graphics}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{tikz-cd}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[export]{adjustbox}

%\usepackage{hyperref}
%\include{connectivity-commands}

\newlength\Colsep
\setlength\Colsep{10pt}
\usetikzlibrary{arrows.meta,
                positioning
                }
%\externaldocument[supp-]{Supplement.tex}


\newcommand{\skcomment}[1]{({\color{blue}{SK's comment:}}\textbf{\color{blue}{#1}})}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}% latexmk will find this if $recorder=0 (however, in that case, it will ignore #1 if it is a .aux or .pdf file etc and it exists! if it doesn't exist, it will appear in the list of dependents regardless)
  \@addtofilelist{#1}% if you want it to appear in \listfiles, not really necessary and latexmk doesn't use this
  \IfFileExists{#1}{}{\typeout{No file #1.}}% latexmk will find this message if #1 doesn't exist (yet)
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
%\newcommand{\comment}[1]{}
\myexternaldocument{Supplement}
\listfiles

\articletype{Research}

\def\taupav{\tau_{\mathrm{Pav}}}

\begin{document}

%\afterpage{%
%   \clearpage % flush any accumulated floats
%   \begin{figure}[ht!]  % or: \begin{table}[ht!]
%   ... % body of figure/table environment
%   \end{figure} % or: \end{table}
%} % end of scope of \afterpage directive



\title{Modelling the cell-type specific mesoscale murine connectome with anterograde tracing experiments}
%\subtitle{mouse connectome} %% Optional subtitle

\author[Koelle et al]% shortened version for running head, optional
{Samson Koelle \affil{1,2}, Jennifer Whitesell \affil{1}, Karla Hirokawa \affil{1},  Hongkui Zeng\affil{1}, Marina Meila\affil{2}, Julie Harris\affil{1}, Stefan Mihalas\affil{1}}

\affiliation{1}{Allen Institute for Brain Science, Seattle, WA, USA}

\affiliation{2}{Department of Statistics, University of Washington, Seattle, WA, USA}

\correspondingauthor{Stefan Mihalas}{stefanm@alleninstitute.org}

\keywords{[a series of capitalized words, separated with commas]}

\begin{abstract}
The Allen Brain Atlas contains of thousands of anterograde tracing experiments targeting diverse structures and classes of projecting neurons.
This paper describes the conversion of these experiments into class-specific connectivity matrices representing the connection between source and target structures.
We introduce and validate a novel statistical model for creation of connectivity matrices that combines spatial and categorical smoothing to share information between similar neuron classes.
We then show that our connectivities display expected cell-type and structure specific connectivities, and factor the wild-type connectivity matrix to uncover the underlying latent structure. 
\end{abstract}

\begin{authorsummary}

\end{authorsummary}

\newpage

\input{connectivity-introduction.tex}
\newpage
\input{connectivity-methods.tex}
\newpage
\input{connectivity-results.tex}
\newpage
\input{connectivity-discussion.tex}

\newpage

\acknowledgments
The Funder and award ID information you input at submission will be introduced by the publisher under a Funding Information head during production.
Please use this space for any additional acknowledgements and verbiage required by your funders.
\newpage
\input{connectivity-supplement.tex}

\newpage
\section{Competing Interests}
\label{sec:comp}
This is an optional section. If you declared a conflict of interest when you submitted your manuscript, please  use this space to provide details about this conflict.

\newpage
\bibliography{bibsamp}

\newpage
\section{Technical Terms}

\textbf{Technical Term} a key term that is mentioned in an NETN article and whose usage and definition may not be familiar across the broad readership of the journal. 


\textbf{Cre-line}  Refers to the combination of cre-recombinase expression in transgenic mouse and cre-induced promotion in the vector that induces labelling of cell-class specific projection. 

\textbf{Cell class} The projecting neurons targeted by a particular cre-line 

\textbf{structural connectivities}  connectivity between structures 

\textbf{Voxel} A $100 \mu m$ cube of brain. 

\textbf{structural connection tensor}  Connectivities between structures given a neuron class

\textbf{dictionary-learning} A family of algorithms for finding low-dimensional data representations.

\textbf{shape constrained estimator} A statistical estimator that fits a function of a particular shape (e.g. monotonic increasing, convex).

\textbf{Nadaraya-Watson} A simple smoothing estimator.

\textbf{connectivity archetypes} Typical connectivity patterns

 \textbf{Expected Loss} Our new estimator that weights different features by their estimated predictive power.
 
%All NETN article types require Technical Terms.

%Identify approximately 10 key terms that are mentioned in your article and whose usage and definition may not be familiar across the broad readership of the journal. 
%Provide brief (20-word or less) definitions for each term, avoiding in these definitions the use of jargon, or highly technical or specialized language. 
%When the article is typeset, the Technical Terms will appear in the margins at or near their first mention in the text.

%In your manuscript, bold the first occurrence of each \textbf{Technical Term} and then provide a list of the terms and their definitions at the end of the manuscript after the references. 


\end{document}


%\newpage
