\documentclass[NETN,manuscript]{stjour-new}
\setcounter{secnumdepth}{1}

%\usepackage{hyperref}
\include{connectivity-commands}

\newlength\Colsep
\setlength\Colsep{10pt}
%\usetikzlibrary{arrows.meta,
%                positioning
%                }
%\externaldocument[supp-]{Supplement.tex}

\newcommand{\smcomment}[1]{({\color{red}{Stefan's comment:}}\textbf{\color{red}{#1}})}
%\newcommand{\skcomment}[1]{({\color{blue}{SK's comment:}}\textbf{\color{blue}{#1}})}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}% latexmk will find this if $recorder=0 (however, in that case, it will ignore #1 if it is a .aux or .pdf file etc and it exists! if it doesn't exist, it will appear in the list of dependents regardless)
  \@addtofilelist{#1}% if you want it to appear in \listfiles, not really necessary and latexmk doesn't use this
  \IfFileExists{#1}{}{\typeout{No file #1.}}% latexmk will find this message if #1 doesn't exist (yet)
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
%\newcommand{\comment}[1]{}
%\myexternaldocument{Supplement}
\listfiles

\articletype{Research}

%\def\taupav{\tau_{\mathrm{Pav}}}

\begin{document}

\title{Modeling the cell-type specific mesoscale murine connectome with anterograde tracing experiments}

\author[Koelle et al]% shortened version for running head, optional
{Samson Koelle \affil{1,2}, Dana Mastrovito \affil{1}, Jennifer D Whitesell \affil{1}, Karla E Hirokawa \affil{1},  Hongkui Zeng\affil{1}, Marina Meila\affil{2}, Julie A Harris\affil{1}, Stefan Mihalas\affil{1}}

\affiliation{1}{Allen Institute for Brain Science, Seattle, WA, USA}

\affiliation{2}{Department of Statistics, University of Washington, Seattle, WA, USA}

\correspondingauthor{Stefan Mihalas}{stefanm@alleninstitute.org}

\keywords{[Connectivity, Cell-type, Mouse]}

\begin{abstract}
The Allen Mouse Brain Connectivity Atlas (MCA) consists of anterograde tracing experiments targeting diverse structures and classes of projecting neurons.
Beyond regional anterograde tracing done in C57BL/6 wild-type mice, a large fraction of experiments are performed using transgenic Cre-lines.
This allows access to cell-class specific whole brain connectivity information, with class defined by the transgenic lines.
However, even though the number of experiments is large, it does not come close to covering all existing cell classes in every area where they exist.
Here, we study how much we can fill in these gaps and estimate the cell-class specific connectivity function given the simplifying assumptions that nearby voxels have smoothly varying projections, but that these projection tensors can change sharply depending on the region and class of the projecting cells.

This paper describes the conversion of Cre-line tracer experiments into class-specific connectivity matrices representing the connection strengths between source and target structures.
We introduce and validate a novel statistical model for creation of connectivity matrices.
We extend the Nadaraya-Watson kernel learning method which we previously used to fill in spatial gaps to also fill in gaps in cell-class connectivity information.
To do this, we construct a "cell-class space" based on class-specific averaged regionalized projections and combine smoothing in 3D space as well as in this abstract space to share information between similar neuron classes.
Using this method we construct a set of connectivity matrices using multiple levels of resolution at which discontinuities in connectivity are assumed. We show that the connectivities obtained from this model display expected cell-type and structure specific connectivities. 
We also show that the wild-type connectivity matrix can be factored using a sparse set of factors, and analyze the informativeness of this latent variable model.

\end{abstract}

\begin{authorsummary}
While standard connectivity studies in mammalian models focus on the overall connection strength between areas, there is an increasing focus on specific connection types between cell classes when describing functions at a local circuit level.
Having recently described the importance of such classes in the cortico-thalamic system, we now investigate their importance for estimating brain-wide mesoscopic connectivity.
Even within our relatively large dataset, the connectivity data across cell classes is sparse, and so we introduce a method to more reliably extrapolate across classes and estimate connection-type specific inter-areal connectivity.
We observe that this complex connectivity may be described via a relatively small set of factors. 
While not complete, this connectivity matrix represents a categorical and quantitative improvement in mouse mesoscale connectivity models.

\end{authorsummary}

\newpage

\input{connectivity-introduction.tex}
\newpage
\input{connectivity-methods.tex}
\newpage
\input{connectivity-results.tex}
\newpage
\input{connectivity-discussion.tex}

\newpage

\acknowledgments
We thank the Allen Institute for Brain Science founder, Paul G. Allen, for his vision, encouragement, and support.  Samson Koelle and Marina Meila have been in part supported by NSF grants DMS 2015272 and DMS 1810975.  Stefan Mihalas has in part been supported by NIH grants 1RF1DA055669-01 and 1R01EB029813-01.
\newpage

\input{connectivity-supplement.tex}

\newpage
\bibliography{connectivity}

\newpage

\section{Technical Terms}

\textbf{Technical Term} a key term that is mentioned in an NETN article and whose usage and definition may not be familiar across the broad readership of the journal. 

\textbf{Cre-line}  The combination of Cre-recombinase expression in transgenic mouse and Cre-induced expression in the vector that induces labelling of projection

\textbf{Cell class} The projecting neurons targeted by a particular Cre-line

\textbf{Structural connectivities} The matrix of connectivities between structures

\textbf{Voxel} A $100 \; \mu m$ cube of brain

\textbf{Structural connection tensor}  Connectivities between structures across cell classes

\textbf{Dictionary-learning} A family of algorithms for finding low-dimensional data representations.

\textbf{Shape constrained estimator} A statistical estimator that fits a function of a particular shape (e.g. monotonic increasing, convex)

\textbf{Nadaraya-Watson} A simple local smoothing estimator with one parameter

\textbf{Connectivity archetypes} Projection patterns from which we can linearly reconstruct the connectome

 \textbf{Expected loss} Our new estimator that weights location against cell-class by their estimated predictive power
 
%All NETN article types require Technical Terms.

%Identify approximately 10 key terms that are mentioned in your article and whose usage and definition may not be familiar across the broad readership of the journal. 
%Provide brief (20-word or less) definitions for each term, avoiding in these definitions the use of jargon, or highly technical or specialized language. 
%When the article is typeset, the Technical Terms will appear in the margins at or near their first mention in the text.

%In your manuscript, bold the first occurrence of each \textbf{Technical Term} and then provide a list of the terms and their definitions at the end of the manuscript after the references. 


\end{document}


%\newpage
